CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
Added subsection for convertsion from discrete to continuous data
-NEEDS TO BE FILLED IN STILL
Added subsection for loss function
Added subsections for additional Conclusions
-Also need to dump results in relevant section.
Filled in subsection for converting data type

@@

\section{Results}
\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{01_loss_graph.png}
      \caption{Average 0/1 Loss for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{precision_graph.png}
      \caption{Average Precision for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{recall_graph.png}
        \caption{Average Recall for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

@@

% Acknowledgements should go at the end, before appendices and references

\acks{1. Davis, Jesse, and Mark Goadrich. "The Relationship between Precision-Recall and ROC Curves." Proceedings of the 23rd International Conference on Machine Learning - ICML 06, 2006, doi:10.1145/1143844.1143874. \\ \\
2. Dietterich, Thomas G. "Machine Learning for Sequential Data: A Review." Lecture Notes in Computer Science Structural, Syntactic, and Statistical Pattern Recognition, 2002, pp. 15-30., doi:10.1007/3-540-70659-32. \\ \\
3. Nédellec, Claire, and Céline Rouveirol, editors. “Machine Learning: ECML-98.” Lecture Notes in Computer Science, Springer Berlin Heidelberg, 1998. pp. 1-2., doi:10.1007/bfb0026664.}

>>>>

\subsection{Converting continuous (discrete) data into categorical}

Since we can’t really deal with continuous attributes when using the Naive Bayes algorithm, we have to convert any continuous (quantitative) data to a categorical format.

We do so on a column by column basis, beginning with checking if the column contains quantitative data or not by seeing if it can be converted to a float. If any one of the elements of that column can’t be converted, it implies the column is of categorical typing.

Once we find  column that we know contains discrete data, we can begin converting it using equal width binning. The equal width binning method finds the smallest and largest values of the quantitative data, subtracts the new found max from the min, and divides the result by the amount of bins. The result is the width of each bin!

From there we simply sort the discrete data into their respective bins in the form of the entire row from the database via the pop() function, and then goes on to convert every value in each respective bin to the value range it belongs to. Value range being the bin bounds. Then the rows are simply recompiled into the database, returned, and repeats this cycle for each column.

Side note: It is fairly obvious we didn't choose this method for it’s efficiency, but rather its simplicity, and consistency.

@@

\subsection{Loss function 2: 0-1 Loss}
-TODO: describe Loss function in a similar function to precision recall.

\section{Results}

\section{Conclusions}
\subsection{Breast Cancer Wisconsin}
\subsection{Glass}
\subsection{Iris}
\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{01_loss_graph.png}
      \caption{Average 0/1 Loss for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{precision_graph.png}
      \caption{Average Precision for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{recall_graph.png}
        \caption{Average Recall for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

@@

\subsection{Soybean}
\subsection{Voting Records}

% Acknowledgements should go at the end, before appendices and references
\acks{1. Davis, Jesse, and Mark Goadrich. "The Relationship between Precision-Recall and ROC Curves." Proceedings of the 23rd International Conference on Machine Learning - ICML 06, 2006, doi:10.1145/1143844.1143874. \\ \\
2. Dietterich, Thomas G. "Machine Learning for Sequential Data: A Review." Lecture Notes in Computer Science Structural, Syntactic, and Statistical Pattern Recognition, 2002, pp. 15-30., doi:10.1007/3-540-70659-32. \\ \\
3. Nédellec, Claire, and Céline Rouveirol, editors. “Machine Learning: ECML-98.” Lecture Notes in Computer Science, Springer Berlin Heidelberg, 1998. pp. 1-2., doi:10.1007/bfb0026664.}
